---
output:
  xaringan::moon_reader:
    seal: false
    css: [mydiy.css,uo-fonts]
    nature:
      slideNumberFormat: "%current%"
      ratio: 16:9
      countIncrementalSlides: true
      titleSlideClass: ["left", "bottom", "my-title"]
    self-contained: ture
---
class: left, bottom, bg1

# <font color = "Gold">Chapter 1 Introduction</font>
## <font color = "white">Haibo Pan</font>
## <font color = "white" size = 5>Dec-9, 2021</font>

---
class: bg2
layout:true
<div class="footer">
<span> 
Copyright &copy 2021. Haibo Pan All rights reserved</span> 
</div>


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```


```{r xaringanExtra, echo = FALSE}
library(xaringanExtra)
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
xaringanExtra::use_search(show_icon = TRUE)
xaringanExtra::use_fit_screen()
xaringanExtra::use_progress_bar(color = "darkred", location = "top")
```

---
class: bg1

## Outline 
.panelset.sideways[
.panel[ .panel-name[Agenda]

- Week1.  R Essentials

- Week2.  R and Data Manipulation

- Week3.  R and Factor Analysis

- Week4.  R and Clustering Analysis

- Week5.  R and ANOVA

- Week6.  R and Regression

- Week7.  R and Probit Model

- Week8.  R and Data Visualization

- Week9.  R and Data Sharing and Presentation

]

.panel[ .panel-name[ILO]

- Coming Soon
]

.panel[ .panel-name[Evaluation]

- Coming Soon

]

.panel[ .panel-name[Requirements]

- Coming Soon
]

]
---
class: center

## What's R 



---
## What's RStudio



---
## What's Packages


---
## What can R do?

---
## R Versus Other Softwares

---

## How to Learn R


---

## Learnning Resources 