---
title: "Data Cleansing"
output:
  bookdown::gitbook
---

```{r settings, echo=F, warning=F,message=F,results=F, comment=""}
knitr::opts_chunk$set(message = F, warning = F)
```

\newpage

# Environment Preparation

<details>

<summary>

Want to see more?

</summary>

```{r}
version
(.packages())
sessionInfo()
rm(list=ls())
```

</details>

```{r}
library(here)
library(data.table) # It is useful for big data
library(sjPlot) # It is useful when the data is very small, for academic research
library(sjmisc) # It is useful when the data is very small, for academic research
library(ggplot2)
library(stargazer)
library(FactoMineR)
```

# Data Import

```{r}
dt1 <- fread(here("e04_data","AB_Financials_98-01_combined_211115.csv"))
```

\newpage

# Data Structure Check {.tabset}

## Data 1 Check

### Classify Variables

Step 2: divide all variables into two groups: categorical variables; numerical variables

### Check Numeric Variables

Step 3: check all numerical variables

### Check Cat Variables

Step 4: Check all categorical variables \[ Cross-table\]

Step 5: Make a Whole Table

# Subset Data
